### 2014-05-02 prevpub.tex
Include merged bibliography

Chapter~\ref{chap:sprout}~revises a previous
publication~\cite{sprout}: Keith Winstein, Anirudh Sivaraman, and Hari
Balakrishnan, ``Stochastic Forecasts Achieve High Throughput and Low
Delay over Cellular Networks,'' \textit{USENIX NSDI~2013}, Lombard,
Ill., April 2013.

Chapter~\ref{chap:remy}~revises a previous publication~\cite{remy}:
Keith Winstein and Hari Balakrishnan, ``TCP ex Machina:
Computer-Generated Congestion Control,'' \textit{ACM SIGCOMM 2013},
Hong Kong, China, August 2013.

Chapter~\ref{chap:learnability}~is adapted from an in-press
submission, to appear as: Anirudh Sivaraman, Keith Winstein, Pratiksha
Thaker, and Hari Balakrishnan, ``An Experimental Study of the
Learnability of Congestion Control,'' \emph{ACM SIGCOMM 2014},
Chicago, Ill., August 2014.

Chapter~\ref{chap:mosh}~revises a previous publication~\cite{mosh}:
Keith Winstein and Hari Balakrishnan, ``Mosh: An Interactive Remote
Shell for Mobile Clients,'' \textit{USENIX Annual Technical Conference
  2012}, Boston, Mass., June 2012.
}

>>>>

Chapter~\ref{chap:sprout}~revises a previous
publication~\cite{sprout}: Keith Winstein, Anirudh Sivaraman, and Hari
Balakrishnan.  \newblock {Stochastic Forecasts Achieve High Throughput
  and Low Delay over Cellular Networks}.  \newblock In {\em NSDI},
2013.

Chapter~\ref{chap:remy}~revises a previous publication~\cite{remy}:
Keith Winstein and Hari Balakrishnan.  \newblock {TCP ex Machina:
  Computer-Generated Congestion Control}.  \newblock In {\em SIGCOMM},
2013.

Chapter~\ref{chap:learnability}~is adapted from a conference
submission that will appear as: Anirudh Sivaraman, Keith Winstein,
Pratiksha Thaker, and Hari Balakrishnan. \newblock {An Experimental
  Study of the Learnability of Congestion Control}. \newblock In {\em
  SIGCOMM}, 2014.

Chapter~\ref{chap:mosh}~revises a previous publication~\cite{mosh}:
Keith Winstein and Hari Balakrishnan.  \newblock {Mosh: An Interactive
  Remote Shell for Mobile Clients}.  \newblock In {\em USENIX Annual
  Technical Conference}, 2012.  }
